### 2020-05-29 paper.tex
Interpretation

Transcripts of informal interviews and ``war stories'' collected from multiple practitioners will give insight in the challenges they face in their day-to-day jobs. We will validate their statement in an observational study and answer our first research question:

@@

\begin{table}[]
	\begin{tabular}{@{}lllll@{}}
	\toprule
					   & \textbf{UI} & \textbf{Integration}                                               & \textbf{Flow Control}                                              & \textbf{RP Runtime} \\ \midrule
	Reactive Inspector & Visual      & Eclipse IDE                                                        & Full                                                               & REScala             \\ \midrule
	rxfiddle           & Visual      & Web App                                                            & \begin{tabular}[c]{@{}l@{}}Visualization\\ Only\end{tabular}       & RxJS                \\ \midrule
	rxjs-spy           & Textual     & \begin{tabular}[c]{@{}l@{}}Browser Console\\and Code\end{tabular} & \begin{tabular}[c]{@{}l@{}}Limited (No\\ Breakpoints)\end{tabular} & RxJS                \\ \midrule
	Rx Visualizer      & Visual      & Web App                                                            & \begin{tabular}[c]{@{}l@{}}Visualization\\ Only\end{tabular}       & RxJS                \\ \bottomrule
	\end{tabular}
	\caption{Feature Matrix for Discussed RP Debugging Tools}
	\label{tab:compare-tools}
	\end{table}

@@

>>>>

Transcripts of informal interviews and ``war stories'' collected from multiple practitioners will give insight in the challenges they face in their day-to-day jobs. We will validate their statements in an observational study and answer our first research question:

@@

\begin{table}[]
	\begin{tabular}{@{}lllll@{}}
	\toprule
					   & \textbf{UI} & \textbf{Integration}                                               & \textbf{Flow Control}                                              & \textbf{RP Runtime} \\ \midrule
	Reactive Inspector & Visual      & Eclipse IDE                                                        & Full                                                               & REScala             \\ \midrule
	rxfiddle           & Visual      & Web App                                                            & None       & RxJS                \\ \midrule
	rxjs-spy           & Textual     & \begin{tabular}[c]{@{}l@{}}Browser Console\\and Code\end{tabular} & Limited & RxJS                \\ \midrule
	Rx Visualizer      & Visual      & Web App                                                            & None       & RxJS                \\ \bottomrule
	\end{tabular}
	\caption{Feature Matrix for Discussed RP Debugging Tools}
	\label{tab:compare-tools}
	\end{table}

@@

We were able to observe how all subjects modified the provided source code manually and augmented it with trace logs at some point. All of them used the produced information in order to track down problems in the application. The the extraction to and reintegration from an external tool was not observed, though would have been yet another form of code modification.

For any subject, we could not identify any contradiction between the observed behavior and the answers given within the after-action survey.

All reviewed subjects exhibited the debugging behavior described in our initial hypothesis which we can accept based on the collected evidence.
